Benchmarking on Rigetti architecture

### 2022-09-29 txt/manuscript.tex
Many minor corrections in section 3.

	\forall E \in \diaguni_2 \,\, | \tr \left(\rho U E\right) | \le \nu. 

@@

	where  for eigenvector $\lambda_1 = e^{i \phi}$ the eigenvector is 

@@

	Whereas, from Theorem 1 in \cite{puchala2018strategies}, we have 

@@

	From Lemma~\ref{lemma:min-e-optimal} we show that 

@@

	\begin{equation}
	\begin{split}
	\| \PP_{U} - \PP_{\Id}  \|_\diamond & =  \max_{\rho \in \Omega_2} \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \|_1   \\ & =  \max_{\rho \in \Omega_2} \| \left( \Id \otimes \sqrt{\rho} \right) \sum_{i=0}^{1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top  \|_1  \\ & = \max_{\rho \in \Omega_2} \| \sum_{i=0}^{1} \proj{i} \otimes \sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \|_1  \\ & = 
	 \max_{\rho \in \Omega_2} \| \sum_{i=0}^{1}\sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \|_1
	\end{split}
	\end{equation}
	We can prove that for all $\alpha, \beta \ge 0 $, and unit vectors $\ket{x}, \ket{y}$ the following equation holds 
	\begin{equation}
	\| \alpha \proj{x} - \beta\proj{y} \|_1 = \sqrt{(\alpha + \beta)^2 - 4\alpha \beta |\braket{x}{y}|^2}.
	\end{equation}
	By taking $\ket{x} = \frac{\sqrt{\rho} \ket{\bar{u_i}}}{\| \sqrt{\rho} \ket{\bar{u_i}} \|}$ and $ \ket{y} = \frac{\sqrt{\rho} \ket{i}}{\|\sqrt{\rho} \ket{i} \|}$ we obtain 
	\begin{equation}
		\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_2} \sum_{i=0}^{1} \sqrt{\left( \bra{u_i} \rho \ket{u_i} + \bra{i} \rho \ket{i }\right)^2 - 4 | \bra{u_i} \rho \ket{i} |^2}.
	\end{equation}
	\todo[inline]{dokonczyc}
	Let us take  $\rho_0 =   \frac{1}{2}  	\left(\begin{array}{cc}1&0\\0&1\end{array}\right)  $,   we obtain
	\begin{equation}
	\begin{split}
	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &= \sum_{i=0}^1  
	\sqrt{\left(\bra{u_i}\rho_0\ket{u_i} + \bra{i} \rho_0 \ket{i} \right)^2 - 
		4|\bra{i}\rho_0\ket{u_i}|^2} = \\& 
	\sum_{i=0}^1  \sqrt{ \braket{i}{i}^2 -  \left| \bra{i}  U \ket{i }\right|^2} = \\ & 
	 \sum_{i=0}^1  \sqrt{\braket{i}{i}^2 -  \left| 1 \cdot \bra{i} \proj{u_1} \ket{i} + 
			e^{i \phi} \cdot\bra{i}  \proj{u_2}\ket{i}\right|^2} =\\&  \sum_{i=0}^1  \sqrt{ 
		\braket{i}{i}^2 -\braket{i}{i}^2\left| \frac{1 + 
			e^{i \phi}}{2}\right|^2} = \\&  \sum_{i=0}^1\braket{i}{i} \sqrt{1 
		-\left| \frac{1+ e^{i \phi}}{2}\right|^2 } = 
	2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } = \frac{|1-e^{i \phi }|}{2}. 
	\end{split}
	\end{equation}
	Due to that, we know  
	that $| \sqrt{\rho}^{\top} \rangle \rangle$ is the discriminator of the problem of discrimination between 
	$\PP_{\Id} $ and $\PP_U$, where 
	$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm ).

	\begin{equation}
		\| \PP_{U} - \PP_{\Id}  \|_\diamond  =  \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \|_1  
=  \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top \rangle  \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1.
	\end{equation}
	So we obtain that \begin{equation}
	\ket{\psi_{AB}} =   | \sqrt{\rho}^\top \rangle  \rangle = \frac{1}{\sqrt{2} } | \Id_2 \rangle \rangle, 
	\end{equation}
	which completes the proof.
\end{proof}

@@

\begin{proof}
From Proposition~\ref{prop-discrim} we have the form of discriminator given by
\begin{equation}
\ket{\psi} = | \sqrt{\rho}^\top \rangle \rangle = \frac{1}{\sqrt{2}} |\Id_2 
\rangle \rangle. 
\end{equation}
From Holevo-Helstrom theorem  we constrain a measurement $\mu$.  
Let us define \begin{equation}
X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi}) -  \left( \PP_\Id 
\otimes \Id_2 \right)(\proj{\psi}).
\end{equation} From 
We consider the Hahn-Jordan decomposition, let \begin{equation}
X = P - Q
\end{equation}
where $P, Q \ge 0 $. Observe, that $P $ and $Q$ are block-diagonal. 
So, let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$, 
respectively. Then  $\Pi_P$ and $\Pi_Q$ have the following forms
\begin{equation}
\Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right) 
\end{equation}
and 
\begin{equation}
\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right) 
\end{equation}
Hence, we define $V_0$ such that
\begin{equation}
\begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
\end{equation}
and $V_1$ such that
\begin{equation}
\begin{cases} 
V_1 \ket{y_p} = \ket{0} \\ 
V_1 \ket{y_q} = \ket{1}
\end{cases} 
\end{equation}
For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H \diag(1, e^{i \phi })H$, the explicit form of $V_0$ and $V_1$ is given by following (see also \texttt{one-qubit.nb}).
The unitary $V_0$ 
has the following form
\begin{equation}
V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
	\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
\end{equation}
whereas the unitary  $V_1$  has the form
\begin{equation}
V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i 
\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} 
\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
\end{equation}
for all $\phi \in [0,2\pi)$. 
Finally, we obtain the measurement $\mu$ of the form
\begin{equation}
\begin{split}
\mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
\proj{0} V_1^\dagger  \\ 
\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
\proj{1} V_1^\dagger  
\end{split}
\end{equation}

>>>>

	\forall_{E \in \diaguni_2} \,\, | \tr \left(\rho U E\right) | \le \nu. 

@@

	where  for eigenvalue $\lambda_1 = e^{i \phi}$, the corresponding 
	eigenvector is 

@@

	From Theorem 1 in~\cite{puchala2018strategies} we have 

@@

	From Lemma~\ref{lemma:min-e-optimal} we know that for our unitary matrix 
	$U =  H \diag(1, e^{i \phi}) H^\dagger$ it also holds that

@@

\begin{equation}
\begin{split}
\| \PP_{U} - \PP_{\Id}  \|_\diamond 
& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \right\|_1   
\\ 
& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
\sum_{i=0}^{1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top  
\right\|_1  \\ 
& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1} \proj{i} \otimes 
\sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1  
\\ 
& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1}\sqrt{\rho}  \left( 
\proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1
\end{split}
\end{equation}
One can prove that for all $\alpha, \beta \ge 0 $, and unit vectors $\ket{x}, 
\ket{y}$ the following equation holds~\cite{watrous} 
\begin{equation}
\| \alpha \proj{x} - \beta\proj{y} \|_1 = \sqrt{(\alpha + \beta)^2 - 4\alpha 
\beta |\braket{x}{y}|^2}.
\end{equation}
By taking $\ket{x} = \frac{\sqrt{\rho} \ket{\bar{u_i}}}{\| \sqrt{\rho} 
\ket{\bar{u_i}} \|}$ and $ \ket{y} = \frac{\sqrt{\rho} \ket{i}}{\|\sqrt{\rho} 
\ket{i} \|}$ we obtain 
\begin{equation}
	\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_2} 
	\sum_{i=0}^{1} \sqrt{\left( \bra{u_i} \rho \ket{u_i} + \bra{i} \rho \ket{i 
	}\right)^2 - 4 | \bra{u_i} \rho \ket{i} |^2}.
\end{equation}
\todo[inline]{dokonczyc}
Let us take  $\rho_0 =   \frac{1}{2}  	
\left(\begin{array}{cc}1&0\\0&1\end{array}\right)  $,   we obtain
\begin{equation}
\begin{split}
||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond 
&= \sum_{i=0}^1  
\sqrt{\left(\bra{u_i}\rho_0\ket{u_i} + \bra{i} \rho_0 \ket{i} \right)^2 - 
4|\bra{i}\rho_0\ket{u_i}|^2}  \\
&= \sum_{i=0}^1  \sqrt{ \braket{i}{i}^2 -  \left| \bra{i}  U \ket{i }\right|^2} 
\\ 
&=\sum_{i=0}^1  \sqrt{\braket{i}{i}^2 -  \left| 1 \cdot \bra{i} \proj{u_1} 
\ket{i} + e^{i \phi} \cdot\bra{i}  \proj{u_2}\ket{i}\right|^2} \\
&= \sum_{i=0}^1  \sqrt{
\braket{i}{i}^2 -\braket{i}{i}^2\left| \frac{1 + e^{i \phi}}{2}\right|^2}  \\
&= \sum_{i=0}^1\braket{i}{i} \sqrt{1 -\left| \frac{1+ e^{i \phi}}{2}\right|^2 } 
= 2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } \\
&= \frac{|1-e^{i \phi }|}{2}.
\end{split}
\end{equation}
Due to that, we know  
that $| \sqrt{\rho}^{\top} \rangle \rangle$ is the discriminator of the problem 
of discrimination between 
$\PP_{\Id} $ and $\PP_U$, where 
$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm 
).

\begin{equation}
\begin{split}
\| \PP_{U} - \PP_{\Id}  \|_\diamond  
&=  \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left( 
\Id \otimes \sqrt{\rho} \right) \|_1 \\
&= \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top 
\rangle \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1.
\end{split}
\end{equation}
So we obtain that \begin{equation}
\ket{\psi_{AB}} =   | \sqrt{\rho}^\top \rangle  \rangle = \frac{1}{\sqrt{2} } | 
\Id_2 \rangle \rangle, 
\end{equation}
which completes the proof.
\end{proof}

@@

\begin{proof}
From Proposition~\ref{prop-discrim} we have the form of discriminator given by
\begin{equation}
\ket{\psi} = | \sqrt{\rho}^\top \rangle \rangle = \frac{1}{\sqrt{2}} |\Id_2 
\rangle \rangle. 
\end{equation}
From Holevo-Helstrom theorem  we constrain a measurement $\mu$.  
Let us define 
\begin{equation}
X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi}) -  \left( \PP_\Id 
\otimes \Id_2 \right)(\proj{\psi}).
\end{equation} 
We consider the Hahn-Jordan decomposition. Let 
\begin{equation}
X = P - Q
\end{equation}
where $P, Q \ge 0 $. Observe, that $P $ and $Q$ are block-diagonal. 
So, let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$, 
respectively. Then  $\Pi_P$ and $\Pi_Q$ have the following forms
\begin{equation}
\Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right) 
\end{equation}
and 
\begin{equation}
\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right). 
\end{equation}
Hence, we define $V_0$ such that
\begin{equation}
\begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
\end{equation}
and $V_1$ such that
\begin{equation}
\begin{cases} 
V_1 \ket{y_p} = \ket{0} \\ 
V_1 \ket{y_q} = \ket{1}
\end{cases}. 
\end{equation}
For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H 
\diag(1, e^{i \phi })H$, the explicit form of $V_0$ and $V_1$ is given as 
follows (see also \texttt{one-qubit.nb}).
The unitary $V_0$ has the form
\begin{equation}
V_0 = \left(
\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)
\end{array}
\right),
\end{equation}
whereas the unitary  $V_1$  has the form
\begin{equation}
V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i 
\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} 
\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right)
\end{equation}
for all $\phi \in [0,2\pi)$. 
Finally, we obtain the measurement $\mu$ of the form
\begin{equation}
\begin{split}
\mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
\proj{0} V_1^\dagger  \\ 
\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
\proj{1} V_1^\dagger.  
\end{split}
\end{equation}
